Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2021-01-04 inst/manuscript/manuscript.Rmd
Added text on label risk correlations

A second measure of the impact of training data error can be obtained by comparing the average label risk per AOI against the model performance metrics....

>>>>

```{r, echo=FALSE}
data("label_risk_metrics")

cor_fun <- function(df) {
  cor.test(df$Risk, df$Score, method = "spearman") %>% broom::tidy()
}

lr_mets <- unique(label_risk_metrics$Metric)
risk_corr <- lapply(lr_mets[lr_mets != "TSS"], function(x) {
  dat <- label_risk_metrics %>% filter(Metric == x)
  cor_fun(dat) %>% mutate(Metric = x)
}) %>% do.call(rbind, .) %>% 
  select(estimate, Metric) %>% 
  rename(r = estimate)
nms <- risk_corr$Metric
risk_corr <- round(t(risk_corr[, 1]), 3)
colnames(risk_corr) <- nms
```

A second measure of the impact of training data error can be obtained by calculating the between the average training label risk per AOI versus various model performance metrics (Table S3). Accuracy had a strong negative association (Spearman's Rank Correlation =  `r risk_corr[, "Accuracy"]` and AUC had a moderate negative association (r = `r risk_corr[, "AUC"]`), while F1 had a weaker positive association (r = `r risk_corr[, "F1"]`). This sign of the latter is counter-intuitive, but relates to the fact that precision was higher in areas of increasing label risk (`r risk_corr[, "Precision"]`), as did false positive error rates (`r risk_corr[, "FPR"]`). In contrast, recall had little correlation with label risk (`r risk_corr[, "Recall"]`), thus the higher precision drove F1 higher, even in areas with more false positives.  **[work on this]**

### 2021-01-04 inst/manuscript/si.Rmd
Added text on label risk correlations

```{r labelrisk_v_metrics, echo=FALSE}

@@

risk_corr <- lapply(unique(risk_metrics$Metric), function(x) {
  dat <- risk_metrics %>% filter(Metric == x)
  cor_fun(dat) %>% mutate(Metric = x)
}) %>% do.call(rbind, .) %>% 
  select(estimate, Metric) %>% 
  rename(r = estimate)
nms <- risk_corr$Metric
risk_corr <- round(t(risk_corr[, 1]), 3)
colnames(risk_corr) <- nms

>>>>

```{r labelrisk_v_metrics, echo=FALSE}
data("label_risk_metrics")

@@

lr_mets <- unique(label_risk_metrics$Metric)
risk_corr <- lapply(lr_mets[lr_mets != "TSS"], function(x) {
  dat <- label_risk_metrics %>% filter(Metric == x)
  cor_fun(dat) %>% mutate(Metric = x)
}) %>% do.call(rbind, .) %>% 
  select(estimate, Metric) %>% 
  rename(r = estimate)
nms <- risk_corr$Metric
risk_corr <- round(t(risk_corr[, 1]), 3)
colnames(risk_corr) <- nms
